### 2020-03-10 README.Rmd
readme correct for everything and higher dpi (120 >> 72). minor correct for change of internal function name

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

```{r eval = F}
n_sims <- 100
n_time_steps <- 100
beta <- .1
gamma <- .03
init_SIR <- c(950, 50, 0)
output_format <- "data.frame"

out <- simulate_SIR_agents(n_sims = n_sims,
                           n_time_steps = n_time_steps,
                           beta = beta, gamma = gamma,
                           init_SIR = init_SIR,
                           output_format = output_format)

df_groups <- out %>% dplyr::group_by(sim) %>%
    agents_to_aggregate_SIR

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 120
)
```

@@

```{r}
n_sims <- 100
n_time_steps <- 100
beta <- .1
gamma <- .03
init_SIR <- c(950, 50, 0)

out <- simulate_SIR_agents(n_sims = n_sims,
                           n_time_steps = n_time_steps,
                           beta = beta, gamma = gamma,
                           init_SIR = init_SIR)

df_groups <- out %>% dplyr::group_by(sim) %>%
    agents_to_aggregate(states = c(tI, tR)) %>%
    rename(S = X0, I = X1, R = X2)
